---
title: "ML_in_wine"
author: "PoMingChen"
date: "2018/11/14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### data preparation
```{r 讀取檔案}
#read.csv is used to read the file that separate the values in comma
#read.csv2 is used to read the file that separate the values in semicolon

read.csv2("./winequality-white.csv") -> whitewine
read.csv2("./winequality-red.csv") -> redwine
```

```{r 製造出紅白酒綜合表格}
library(tidyverse)
library(magrittr)
whitewine
whitewine %>% mutate(color = "white") -> whitewine
redwine %>% mutate(color = "red") -> redwine

rbind(whitewine, redwine) -> winelist

winelist %<>% mutate(white = if_else(color=="white", 1, 0))
winelist %<>% select(color, white, quality, everything())
```

```{r 創造優/劣的虛擬變數}
winelist %<>% mutate(good = if_else(quality >= 6, "Good","Bad")) %<>% 
             select(color, white, quality, good, everything())
```

#### the caret package tool
> The caret package (short for _C_lassification _A_nd _RE_gression _T_raining) is a set of functions that attempt to streamline the process for creating predictive models. The package contains tools for:

- data splitting
- pre-processing
- feature selection
- model tuning using resampling
- variable importance estimation
```{r}
install.packages("caret")
```

```{r}
#the initiated setting in the beginning

# library(doParallel)
# cl = makeCluster(7)
# registerDoParallel(cl)
```

```{r 切割樣本}
library(caret)
set.seed(1234) # so that the indices will be the same when re-run

trainIndices = createDataPartition(winelist$good, p=.8, list=F)

trainIndices
#logical - should the results be in a list (TRUE) or a matrix with the number of rows equal to floor(p * length(y)) and times columns.

#free.sulfur.dioxide和total.sulfur.dixocide共線程度高，因此留一個即可。
wine_train = winelist %>% 
  select(-free.sulfur.dioxide, -density, -quality, -color, -white) %>% 
  slice(trainIndices)

#slice : Select rows by position；filter的話就是會有一個equivalent operation

wine_test = winelist %>% 
  select(-free.sulfur.dioxide, -density, -quality, -color, -white) %>% 
  slice(-trainIndices)
```

```{r 資料型態轉換}
wine_train #5,199 rows
wine_test #1,298 rows

wine_train[,2:10] <- lapply(wine_train[,2:10], function(x) as.numeric(as.character(x)))
wine_test[,2:10] <- lapply(wine_test[,2:10], function(x) as.numeric(as.character(x)))

# wine_train[complete.cases(wine_train),]
# wine_test[complete.cases(wine_test),]
```

let's have the short visual play (prepoccessed-data)
```{r }
wine_trainplot = select(wine_train, -good) %>% 
  preProcess(method="range") %>% 
  predict(newdata= select(wine_train, -good))
#Pre-processing transformation (centering, scaling etc.) can be estimated from the training data and applied to any data set with the same variables.

#The "range" transformation scales the data to be within rangeBounds. If new samples have values larger or smaller than those in the training set, values will be outside of this range.

```

```{r}
wine_trainplot
featurePlot(x=wine_trainplot, y=wine_train$good, "box")
```

```{r}
# x <- matrix(rnorm(50*5),ncol=5)
# y <- factor(rep(c("A", "B"),  25))
# 
# x
# y
# featurePlot(x, y, "box")
```

